### 2025-09-18 README.Rmd
Update citation and readme for publiication

[![publication](https://img.shields.io/badge/Cite-Unpublished-yellow)](https://github.com/bmait101/hatchR/blob/master/inst/CITATION)
[![downloads](https://cranlogs.r-pkg.org/badges/hatchR)](https://cran.r-project.org/package=hatchR)
[![total](https://cranlogs.r-pkg.org/badges/grand-total/hatchR)](https://cranlogs.r-pkg.org/)

@@

A manuscript accompanying this package is *in press* at *Fisheries*, forthcoming this Fall.

>>>>

[![publication](https://img.shields.io/badge/Cite-Fisheries_2025-green)](https://doi.org/10.1093/fshmag/vuaf078)
[![downloads](https://cranlogs.r-pkg.org/badges/hatchR)](https://cran.r-project.org/package=hatchR)
[![total](https://cranlogs.r-pkg.org/badges/grand-total/hatchR)](https://cranlogs.r-pkg.org/)

@@
